---
title: "OkCupid"
author: "Project 5"
date: "November 30, 2017"
output: html_document
---

# Set-Up

Install Packages:

```{r}
#install.packages("fmsb")

library(fmsb)
```

Load Data:

```{r}
raw.data.speed.dating <- read.csv("../data/speed-dating-experiment/Speed Dating Data.csv")
load("../data/profiles.RDA")
```

# Data Description

The speed dating data set is...

# Data Filter

Relevant Data:

```{r}
#For looking at matches
select.fields <- c("match", "gender", "int_corr", "samerace", "race")
speed.dating <- raw.data.speed.dating[ , select.fields]


#For looking at individuals
select.fields2 <- c("iid", "gender", "race", "imprace", "imprelig", "age",
                    "income", "goal", "date", "go_out", "career_c", "sports", 
                    "dining", "museums", "art", "gaming", "clubbing", "reading", 
                    "music", "yoga", "attr1_1", "sinc1_1", "intel1_1", "fun1_1",
                    "amb1_1", "shar1_1")

speed.dating.individual <- raw.data.speed.dating[ , select.fields2]
speed.dating.individual <- unique(speed.dating.individual)

rm(select.fields, select.fields2)
```

Calculate matching rates for individuals and merge with individuals dataset:

```{r}
matching.rates <- raw.data.speed.dating[, c("match", "iid")]
matching.rates <- aggregate(match ~ iid, data = matching.rates, mean)

speed.dating.individual <- merge(speed.dating.individual, matching.rates, by = "iid")
```

# Data Analysis

Preliminary Analysis:

```{r}
#For every variable 1 = yes and 0 = no
#For every rate, 10 is important and 0 is not important

#Matching analysis-----------------------------------------------------------------------

  #Matching percentage
  round(sum(speed.dating$match == 1)/nrow(speed.dating) * 100, 2)
  
  #Box plot on matches by ratings of interest correlations
  par(mfrow=c(1,2))
  boxplot(int_corr ~ match, data = speed.dating, main = "Correlation on ratings of interests x Match")
  boxplot(speed.dating$int_corr, main = "Correlation on ratings of interests")
  
  #Race
  table(speed.dating$match, speed.dating$samerace)
  length(unique(speed.dating$race))
  table(speed.dating$race, speed.dating$match)

#Individual analysis (taking repeated rows)-----------------------------------------------

  #How important it is to be with someone of the same religion or race
  par(mfrow=c(1,2))
  boxplot(speed.dating.individual$imprace, main = "Same race/ethnic background  rating")
  boxplot(speed.dating.individual$imprelig, main = "Same religion rating")
  
  #Matching rates
  boxplot(speed.dating.individual$match, main = "Matching rates")
  
  #What people are looking for in his partner
  par(mfrow=c(1,1))
  radar <- apply(speed.dating.individual[,c("attr1_1","sinc1_1","intel1_1","fun1_1","amb1_1","shar1_1")], 2, mean, na.rm = T)
  names(radar) <- c("Attractive", "Sincere", "Inteligent", "Fun", "Ambitious", "Shared Hobbies")
  radar <- rbind( rep(30,6), rep(0,6), radar)
  radarchart(as.data.frame(radar), title = "What people are looking for")
  
  par(mfrow=c(1,2))
  radar <- apply(speed.dating.individual[speed.dating.individual$gender == 0, c("attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1", "shar1_1")], 2, mean, na.rm = T)
  
  names(radar) <- c("Attractive", "Sincere", "Inteligent", "Fun", "Ambitious", "Shared Hobbies")
  radar <- rbind( rep(30,6), rep(0,6), radar)
  radarchart(as.data.frame(radar), title = "What women are looking for")
  
  radar <- apply(speed.dating.individual[speed.dating.individual$gender == 1, c("attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1", "shar1_1")], 2, mean, na.rm = T)
  
  names(radar) <- c("Attractive", "Sincere", "Inteligent", "Fun", "Ambitious", "Shared Hobbies")
  radar <- rbind( rep(30,6), rep(0,6), radar)
  radarchart(as.data.frame(radar), title = "What men are looking for")
```

Is there any pattern among people with high match rates?

Can we predict someone's matching rate?

Can we cluster matches?

Can we predict whether 2 people will match? 








